Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2022-11-09 rmd/cover_letter.Rmd
edit

We are excited to submit our manuscript entitled "Ecosystem size and complexity are extrinsic drivers of food chain length in branching networks" for consideration for publication in The American Naturalist.

>>>>

We are excited to submit our manuscript entitled "*Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems*" for consideration.

### 2022-11-09 rmd/manuscript.Rmd
edit

---
title: "Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems"
output:
  pdf_document:
    latex_engine: xelatex
  #word_document:
  #  reference_docx: word_format.docx
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: references.bib
csl: https://www.zotero.org/styles/ecosphere
mainfont: Times New Roman
header-includes:
  \usepackage{textgreek}
---

@@

Before the main simulation, we performed an extensive sensitivity analysis to identify influential parameters (see **Supplementary Text** and **Table S1 -- S3**). Our sensitivity analysis revealed that ecosystem size and/or complexity effects were sensitive to disturbance, productivity, dispersal, and omnivory. Therefore, we ran the main simulation with `r n_scenario` parameter sets differing in these ecological contexts (two levels of disturbance, two levels of productivity, two levels of dispersal distance, and three levels of omnivory) and parameter values were summarized in **Table S1**.

>>>>

---
title: "Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems"
output:
  pdf_document:
    latex_engine: xelatex
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: references.bib
csl: https://www.zotero.org/styles/ecosphere
mainfont: Times New Roman
header-includes:
  \usepackage{lineno, textgreek}
  \linenumbers
---

@@

Before the main simulation, we performed an extensive sensitivity analysis to identify influential parameters (see **Table1**, **Supplementary Text,** and **Table S1 -- S2**). Our sensitivity analysis revealed that ecosystem size and/or complexity effects were sensitive to disturbance, productivity, dispersal, and omnivory. Therefore, we ran the main simulation with `r n_scenario` parameter sets differing in these ecological contexts (two levels of disturbance, two levels of productivity, two levels of dispersal distance, and three levels of omnivory) and parameter values were summarized in **Table 1**.
